\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{classic}
% possible styles : 'casual' (by default),
% 'classic', 'oldstyle' and 'banking'
\moderncvcolor{orange}
% possible colors : 'blue' (by default),
% 'orange', 'green', 'red', 'purple', 'grey' and 'black'
\usepackage[top=1.0cm, bottom=1.0cm, left=1.6cm, right=1.6cm]{geometry}
\usepackage{helvet}
\usepackage[utf8]{inputenc}

% personal data
\name{Tom}{Moulard}
\title{Software Developer}
\email{tom@moulard.org}
\homepage{tom.moulard.org}
\address{2, street gu\'ebriant}{75020 Paris}{France}
\phone[mobile]{\href{tel:+33-6-51-48-72-60}{+33 6 51 48 72 60}}
\social[linkedin]{tommoulard}
\social[github]{tommoulard}
% \extrainfo{Permis B}
% \quote{"Our virtues and our failings are inseparable, like force and matter.
% When they separate, man is no more" Nikola Tesla}

\begin{document}
\makecvtitle
\vspace*{-10mm}

\section{Objectives}
Seeking to apply my analytical skills to the challenges posed by an internship
at your company. Poses proven algorithmic and research abilities that will
aid your company in meeting its milestones.

\section{Education}
% \cventry{years}{degree}{institution}{location}{grade}{description}
\cventry{2014-date}{EPITA}{Computer Engineering}{FR}{}{}
\cventry{2014-2019}{UPEC}{Computer Engineering focused School}{FR}{}{}
% \cventry{2018}{Google}{Q{\&}A Meeting with an Google Software Engineer.}{FR}{}{}
\cventry{2017}{BJTU}{Computer Engineering}{ZH}{}{}
% \cventry{2014}{BNSSA and PSE1}{lifeguard}{}{}{}
\cventry{2014}{High School diploma}{Scientific section}{}{}{}

\section{Work}
% \cventry{}{}{}{}{}{}
% \cventry{years}{position}{company}{location}{length}{description}
\cventry{2019-date}{Co-Funder and CTO}{Eiko}{FR}{}{
Creating a Progressive Web App using:
\begin{itemize}
	\item Back-end: Go, GCP and Algolia;
	\item Front-end: HTML, CSS, JS and materializecss.
\end{itemize}
}
\cventry{2018}{Full Stack}{Zeodine}{FR}{4 month}{
Creating a web site using:
\begin{itemize}
	\item Back-end: Go;
	\item Front-end: HTML, CSS, JS and P5.js.
\end{itemize}
And using: Unit Testing; Acceptance Testing; Automatic Deployment.
}
\cventry{2017}{Python Developer}{Chinese Environment Ministry}{ZH}{2 month}{
Natural Language Processing in Python and graph database management (Neo4j).
}
\cventry{2017}{Internship}{Orange}{FR}{1 month}{
pfsense firewall managing inside an OpenStack cloud
(High Availability, tunneling, sorting).
}
%\cventry{2015}{Lifeguard}{Abyssea}{FR}{1 month}{}

\section{Projects}
% \cventry{years}{project name}{language}{link}{length}{description}
\cventry{2019}{Web Server}{C++}{\href{https://github.com/tommoulard/sws}{link}}
{7 weeks}{Spider Web Server is a pedagogical project. Spider is an HTTP server}
%\cventry{2019}{Virtual Switch}{C}
%{\href{https://github.com/tommoulard/myvswitch}{link}}{2 weeks}{
%Implementation of virtual switch. With a notion of vlans and Port mirroring.
%}
% \cventry{2018}{Malloc}{C}
% {\href{https://github.com/tommoulard/malloc}{link}}{1 weeks}{
% Memory allocator without any call to sbrk
% }

\section{Skills}
\cventry{Languages}{Python, C, Golang, shell}{}
{Java, C++, C\#, OCamL, JS, SQL}{}{}
\cventry{Tools}{Docker, GIT, CircleCI, Django, Ansible, Terraform}{}
{Docker-compose, Unity, MongoDB, Neo4j, MySQL, PostgreSQL, VirtualBox,
Agouti, Traefik, Apache, Hugo}{}{}
\cventry{Markup}{{\LaTeX}}{}{HTML, CSS, YAML, toml}{}{}
\cventry{Multimedia}{Word, Excel, Access, PowerPoint}{}
{GIMP, Imagemagick, Inkscape}{}{}
\cventry{Languages}{French, English}{}{Spanish, Chinese}{}{
Native, Fluent (TOEIC: 945/990), Writing and Speaking, Low understanding
}
% \subsection{Languages}
% \cvitemwithcomment{Language}{Level}{Comments}
% \cvlanguage{French}{Native}{}
% \cvlanguage{English}{Fluent}{TOEIC: 945/990}
% \cvlanguage{Spanish}{Writing and speaking}{}
% \cvlanguage{Chinese}{Low understanding}{}
% \cventry{Additionnal}{Lifeguard}{Since 2014}{}{}{}

\section{Interests}
\cvitem{Technology}{Open Source fondations; Robotics; drones;
physical/digital interfaces; human interaction.}
\cvitem{Environment}{Social impact and responsibility; influence of technology.}
\cvitem{Sports}{Swimming; Badminton; Roller.}
\end{document}
